The \texttt{R1} is a ref to another node, \texttt{F1}, ref to local
node, \texttt{L1}, ref to local node of the \texttt{R1}, M1, ref to
local node of an element of \texttt{R1} of a node that has a \texttt{L1}
ref.

Sample of of a units file.

\begin{verbatim}
----------------------------------------------------------------
Comp Attr parent Type FindIn
----------------------------------------------------------------

    Element table    R1 Type             * Pointer to (Type).
    Element relation C1 WORD             * Relation type
    Element name     C1 NAME             * Colomn name.

Ref table Type check

----------------------------------------------------------------
Comp Where parent Type
----------------------------------------------------------------

    Element attr     F1 Attr      * Field name
    Element from_id  M1 Attr      * From id

Ref     attr Attr check
Ref3 from_id Attr attr Attr table check
\end{verbatim}

The \texttt{Ref3} uses the \texttt{M1} field \texttt{from\_id}. The link
goes to node of type \texttt{Attr}. It uses the \texttt{attr} field to
get to \texttt{Attr} node. In that node it uses the \texttt{table} field
to be used as the parent \texttt{(Type)} to find the \texttt{Attr} in.
The \texttt{from\_id,\ attr} can be different node types. The refs run
in a sequence at \texttt{Element} level. First it does the
\texttt{F1,\ R1} ones, then the the \texttt{M1,\ L1} ones.

Sample of def file.

\begin{verbatim}
--------------------------------------------------------
Type User User
--------------------------------------------------------

Attr Contractor_employee     view contractor_name

Where contractor_name  id_number = contractor_id

---------------------------------------------
Type Contractor_employee Contractor Employee
---------------------------------------------

Attr . . id_number
\end{verbatim}

If this data had to be loaded into a database, the foreign links need to
be populated. Need select statements to get to the id's for this. The
loader's refs does this.

\begin{verbatim}
Attr.tablep = Select id from type where name = 'Contractor_employee'
Where.attrp = Select id from attr where name = 'contractor_name' and attr.parentp = parentp
Where.from_idp = Select id from attr where name = 'id_number' and attr.parentp = Atrr[ Where.attrp ].tablep
\end{verbatim}

To use the links from the \texttt{Where} node, use
\texttt{attr,from\_id,id}. To use it from the \texttt{Attr} node, use
\texttt{Where\_attr,\ Where\_from\_id,\ Where\_id}. These are the
reverse links that loops to match. The \texttt{Its} cmd will get them
all, The variables will get the first one.

The \texttt{L1} is a simpler model of this, it uses the \texttt{R1}
instead of the \texttt{F1} to get to the parent. The \texttt{F1} share
the same parent. The \texttt{R1} finds the parent - top level nodes.

The \texttt{check} on the refs, means it is an error if it does find the
link. A \texttt{(.)} here, means it is optional link. The value then
also need to be a \texttt{(.)} if it is optional. If the value if
different, then it is an error if not found. A \texttt{(?)} here means
link if can, but no error if not.
